Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/prov.tex
similarities Minerva + Providence

Notice that for $j\ge 2$, unlike $\tau_j$, computing $\omega_j$ requires no convolution and is hence computationally considerably more efficient.

>>>>

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive.

Notice also that \Providence and \Minerva are identical for $j=1$.
